---
title: "Week-5"
output:
  pdf_document: default
  html_notebook: default
author: QuickFixDemos 
---
Packages Used Installation
```{r}
# install.packages("e1071") 
# install.packages("caTools") 
# install.packages("caret") 
# install.packages("bnlearn")
```
```{r}
library(bnlearn)
library(e1071) 
library(caTools) 
library(caret) 
```
Lab Assignment 5

Learning Objective:
Understand the graphical models for inference under uncertainty, build Bayesian Network in R, Learn the structure and CPTs from Data, naive Bayes classification with dependency between features. 
Problem Statement:
A table containing grades earned by students in respective courses is made available to you in (codes folder) 2020_bn_nb_data.txt. 
Q1: Consider grades earned in each of the courses as random variables and learn the dependencies between courses. 
##Solution
```{r}
dataset<-read.table("C:/Users/shiva/OneDrive/Desktop/Semester-6/AILab/Lab5/2020_bn_nb_data.txt",head=TRUE,stringsAsFactors=TRUE)
dataset_grades=dataset
dataset_grades= subset(dataset_grades, select = -c(QP) )
dataset_net<-hc(dataset_grades,score="k2")
dataset_net
plot(dataset_net)
```
Q2: Using the data, learn the CPTs for each course node.
```{r}
dataset_net_bn_fit <- bn.fit(dataset_net, dataset_grades )
print(dataset_net_bn_fit)
```
Q3: What grade will a student get in PH100 if he earns DD in EC100, CC in IT101 and CD in MA101.
```{r}
grade_list <- list("AA","AB","BB","BC","CC","CD","DD","F")
probability <- 0.0
result=""
for(grade in grade_list) {
  prob <- cpquery(dataset_net_bn_fit, event = (PH100== grade), evidence = (EC100=="DD" & IT101=="CC" & MA101=="CD"))
  if(probability<prob){
    probability=prob;
    result=grade
  }
}
sprintf("The max probability of resultant grade is %f",probability)
sprintf("The max grade obtained with given ecidence is %s ",result)
```
Q4(a): The last column in the data file indicates whether a student qualifies for an internship program or not. From the given data, take 70 percent data for training and build a naive Bayes classifier (considering that the grades earned in different courses are independent of each other) which takes in the student’s performance and returns the qualification status with a probability. Test your classifier on the remaining 30 percent data. Repeat this experiment for 20 random selection of training and testing data. Report results about the accuracy of your classifier.
```{r}
dataset_grades=dataset
split <- sample.split(dataset_grades, SplitRatio = 0.7) 
train <- subset(dataset_grades, split == "TRUE") 
test <- subset(dataset_grades, split == "FALSE") 
naive_bayes_classifier<- naiveBayes(QP ~ ., data = train)
y_train=predict(naive_bayes_classifier, newdata = train)
y_prediction <- predict(naive_bayes_classifier, newdata = test)
print("Train Accuracy")
cm_train<- table(train$QP, y_train)
confusionMatrix(cm_train)
print("Test Accuracy")
cm_test <- table(test$QP, y_prediction)
confusionMatrix(cm_test)
```
Q4(b): Repeat this experiment for 20 random selection of training and testing data. Report results about the accuracy of your classifier.
```{r}
dataset_grades=dataset
dataset_grades=dataset_grades[sample(nrow(dataset_grades), 20), ]
split <- sample.split(dataset_grades, SplitRatio = 0.7) 
train <- subset(dataset_grades, split == "TRUE") 
test <- subset(dataset_grades, split == "FALSE")
naive_bayes_classifier<- naiveBayes(QP ~ ., data = train)
y_train=predict(naive_bayes_classifier, newdata = train)
y_prediction <- predict(naive_bayes_classifier, newdata = test)
print("Train Accuracy")
cm_train<- table(train$QP, y_train)
confusionMatrix(cm_train)
print("Test Accuracy")
cm_test <- table(test$QP, y_prediction)
confusionMatrix(cm_test)
```

Q5(a): Repeat 4, considering that the grades earned in different courses may be dependent.
```{r}
dataset_grades=dataset
split <- sample.split(dataset_grades, SplitRatio = 0.7) 
train <- subset(dataset_grades, split == "TRUE") 
test <- subset(dataset_grades, split == "FALSE") 
naive_bayes_classifier<- bn.fit(hc(train, score="k2"), train)
y_train=predict(naive_bayes_classifier,node="QP", data = train)
y_prediction <- predict(naive_bayes_classifier,node="QP", data = test)
print("Train Accuracy")
cm_train<- table(train$QP, y_train)
confusionMatrix(cm_train)
print("Test Accuracy")
cm_test <- table(test$QP, y_prediction)
confusionMatrix(cm_test)
```
Q5(b): Repeat this experiment for 20 random selection of training and testing data. Report results about the accuracy of your classifier.
```{r}
dataset_grades=dataset
dataset_grades=dataset_grades[sample(nrow(dataset_grades), 20), ]
split <- sample.split(dataset_grades, SplitRatio = 0.7) 
train <- subset(dataset_grades, split == "TRUE") 
test <- subset(dataset_grades, split == "FALSE")
naive_bayes_classifier<- bn.fit(hc(train, score="k2"), train)
y_train=predict(naive_bayes_classifier,node="QP", data = train)
y_prediction <- predict(naive_bayes_classifier,node="QP", data = test)
print("Train Accuracy")
cm_train<- table(train$QP, y_train)
confusionMatrix(cm_train)
print("Test Accuracy")
cm_test <- table(test$QP, y_prediction)
confusionMatrix(cm_test)
```
